---
title: "The Course Project in Practical Machine Learning"
author: "Atsuko Yamamoto"
date: "April 26, 2015"
output: html_document
---
## Executive Summary
This is the Course Project for the class "Practical Machine Learning".
In this report, I predict the manner using the exercise data from accelerometers on the belt, forearm, arm and dumbell of  6 participants.
I build the prediction model to predict the objective variable "classe".

## Result
I use caret with random forest as my model with 5 fold cross validation. 
The model is mtry : 27, accuracy : 0.99, OOB estimate of  error rate is less than 1%. 

Predictions of testing:
B A B A A E D B A A B C B A E E A B B B

### Data preprocessing
```{r,echo=FALSE}
setwd("~/Rdata/MachineLearning/Projects")
```

```{r loading}
# loading data
temp <- tempfile()
urltrain="https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
urltest="https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
download.file(urltrain,temp,"curl")
pmltrain <- read.csv(temp)
download.file(urltest,temp,"curl")
pmltest <- read.csv(temp)
dim(pmltrain);dim(pmltest)
# summary(pmltrain)
```
There are a lot of missing values in csvfiles.
I get rid of the clumns that are independent of exercizes and mostly NA.
```{r Cleaning}
# Cleaning the data
pmldata <- pmltrain[,-1:-7]
naCnt <- apply(pmldata,2,function(x) {sum(is.na(x)|x=="")})
pmldata <- pmldata[,which(naCnt < 19216)]
dim(pmldata)
```

### Data splitting
Devide the pmldata between training and testing.
```{r splitting}
library(caret)
set.seed(1000)
inTrain <- createDataPartition(y=pmldata$classe, p=0.6, list=FALSE)
training <- pmldata[inTrain,]
testing <- pmldata[-inTrain,]
dim(training); dim(testing)
```

### Training
I use caret with random forest as my model with 5 fold cross validation. Because random forests are usually one of the top performing algorithms along with boosting in any prediction contests.
```{r training}
rfmodel <- train(classe ~ .,method="rf", data=training,
                 trControl=trainControl(method="cv", number=5),
                 prox=TRUE, allowParallel=TRUE)
rfmodel
rfmodel$finalModel
```

```{r predicting}
pred <- predict(rfmodel, testing)
table(pred, testing$classe)
```
The model is mtry = 27, and accuracy is 0.99.
OOB estimate of  error rate is less than 1%. 
That is a good model.

### Predictions of testing
I use my prediction model to predict 20 different test cases.
```{r predictingtest}
answers <- predict(rfmodel, pmltest)
answers
```
